\documentclass[11pt]{article}
\usepackage{acl2016}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}

\usepackage{todonotes}
\usepackage{newclude}
\usepackage{float}

\def\MV#1{\textcolor{red}{TODO: \textit{#1}}}
\def\subsubsubsection#1{\subsubsection*{#1}}

\aclfinalcopy% Uncomment this line for the final submission
%\def\aclpaperid{***} %  Enter the acl Paper ID here


\newcommand\BibTeX{B{\sc ib}\TeX}

\title{Extracting Knowledge from Dialogue}

\author{Ondřej Plátek \\
  Charles University in Prague, Faculty of Mathematics and Physics \\
  Institute of Formal and Applied Linguistics \\
  Malostranské náměstí 25, 11800 Praha 1, Czech Republic\\
  {\tt oplatek@ufal.mff.cuni.cz}\\}

\date{}



\begin{document}
\maketitle
\begin{abstract}
Building a conversation agent is a demanding process which is typically simplified by narrowing the domain of conversation and fixing the knowledge about which is the agent able to communicate.
The research so far focused on optimizing the agent either online using very weak feedback or using supervised learning and annotation.
This work focuses on designing the conversational agents which will be able to:
\begin{itemize}
    \item collect explicit annotation interactively during the dialogue,
    \item enhancing the knowledge base of a system by new facts,
    \item learn better reward signals from conversations.
\end{itemize}
By implementing these properties we aim at reducing the amount of data and annotation needed for developing a conversational agent.
We would also like to explore how to improve the agent over time.
\end{abstract}

\section{Introduction}
\label{sec:introduction}

I need to set it up with relevant work e.g.~\cite{young2010hidden}.

First, we discuss approaches to XY in Section~\ref{sec:}. 
Second, ongoing work on approach XY is described  in~Section. 
Third, we propose future work in Section~\ref{sec:}.
Finally, we discuss importance of our work in the future in Section~\ref{sec:}.




\section{Discussion}
\label{sec:discussion}

\section*{Acknowledgments}
This research was partly funded by the Ministry of Education, Youth and Sports of the Czech Republic under the grant agreement LK11221, core research funding, grant GAUK 1915/2015, and also partially supported by SVV project number 260 333. 
We gratefully acknowledge the support of NVIDIA Corporation with the donation of the Tesla K40c GPU used for this research.
Computational resources were provided by the CESNET LM2015042 and the CERIT Scientific Cloud LM2015085, provided under the programme ``Projects of Large Research, Development, and Innovations Infrastructures''.

\bibliographystyle{acl2016}
\bibliography{bibliography}


\end{document}
